Estimating duration using survival analysis

### 2024-03-22 cis-perfect-testing.tex
typo fix

Doubly interval censored and truncated data are common when assessing the survival time of bird and insect nests~\autocite{heiseyABCs}.
\textcite{heiseyModelling}, building on on long-standing methodology~\autocite{dempsterMaximum,turnbullEmpirical}, develops a likelihood-based inference framework, allowing for arbitrary truncation patterns and double interval censoring.
They apply it to a situation where the visit times (possible detection times) are common to all the individuals, simplifying the likelihood.
I adapt this framework for CIS, when each individual has their own visit schedule (see section \cref{perf-test:sec:model}).

>>>>

Doubly interval censored and truncated data are common when assessing the survival time of bird and insect nests~\autocite{heiseyABCs}.
\textcite{heiseyModelling}, building on long-standing methodology~\autocite{dempsterMaximum,turnbullEmpirical}, develops a likelihood-based inference framework, allowing for arbitrary truncation patterns and double interval censoring.
They apply it to a situation where the visit times (possible detection times) are common to all the individuals, simplifying the likelihood.
I adapt this framework for CIS, when each individual has their own visit schedule (see section \cref{perf-test:sec:model}).
